### 2024-05-26 getting-started.qmd
20240526 - comment out 4th down data
20240526 - shrink file size

```{r}
nfl_4thdown <- nfl4th::load_4th_pbp(seasons = 2014:2023)
```

@@

```{r}
subsetVars <- c("status","display_name","college_name")

@@

```{r}
dropVars <- c("status","college_name")

@@

```{r}
nfl_players %>%
  select(status, display_name, college_name)

@@

```{r}
nfl_players %>%
  select(-status, -college_name)

@@

```{r}
subsetRows <- c(1,3,5)

@@

```{r}
nfl_players %>%
  filter(position_group == "RB")

@@

```{r}
nfl_players[c(1,3,5), c(1,2,3)]
nfl_players[subsetRows, subsetVars]
nfl_players[which(nfl_players$position_group == "RB"), subsetVars]
```

@@

```{r}
nfl_players %>%
  filter(position_group == "RB") %>%
  select(all_of(subsetVars))
```

@@

```{r}
nfl_actualStats_offense_weekly

dim(nfl_actualStats_offense_weekly)

@@

```{r}
nfl_players

dim(nfl_players)

@@

```{r}
fullJoinData <- full_join(
  nfl_actualStats_offense_weekly,
  nfl_players,
  by = c("player_id" = "gsis_id"))

fullJoinData
dim(fullJoinData)
```

@@

```{r}
leftJoinData <- left_join(
  nfl_actualStats_offense_weekly,
  nfl_players,
  by = c("player_id" = "gsis_id"))

leftJoinData
dim(leftJoinData)
```

@@

```{r}
rightJoinData <- right_join(
  nfl_actualStats_offense_weekly,
  nfl_players,
  by = c("player_id" = "gsis_id"))

rightJoinData
dim(rightJoinData)
```

@@

```{r}
innerJoinData <- inner_join(
  nfl_actualStats_offense_weekly,
  nfl_players,
  by = c("player_id" = "gsis_id"))

innerJoinData
dim(innerJoinData)
```

@@

```{r}
semiJoinData <- semi_join(
  nfl_actualStats_offense_weekly,
  nfl_players,
  by = c("player_id" = "gsis_id"))

semiJoinData
dim(semiJoinData)
```

@@

```{r}
antiJoinData <- anti_join(
  nfl_actualStats_offense_weekly,
  nfl_players,
  by = c("player_id" = "gsis_id"))

antiJoinData
dim(antiJoinData)
```

@@

```{r}
crossJoinData <- cross_join(
  unique(nfl_actualStats_offense_weekly[,c("player_id","player_display_name")]),
  data.frame(season = 2020:2024))

@@

```{r}
dataLong <- nfl_actualStats_offense_weekly %>% 
  select(player_id, player_display_name, season, week, fantasy_points)

dataLong
```

@@

```{r}
dataLong %>% 
  pivot_wider(
    names_from = week,
    names_glue = "{.value}_week{week}",
    values_from = fantasy_points)

dataLong %>% 
  pivot_wider(
    names_from = c(season, week),
    names_glue = "{.value}_{season}_week{week}",
    values_from = fantasy_points)
```

@@

```{r}
dataWide <- nfl_actualStats_offense_weekly %>% 
  select(player_id, player_display_name, season, week, recent_team, opponent_team)

dataWide
```

@@

```{r}
dataWide %>% 
  pivot_longer(
    cols = c(recent_team, opponent_team),
    names_to = "role",
    values_to = "team")
```

>>>>

nfl_4thdown <- nfl4th::load_4th_pbp(seasons = 2014:2023)
```

@@

subsetVars <- c("status","display_name","college_name")

@@

dropVars <- c("status","college_name")

@@

nfl_players %>%
  select(status, display_name, college_name)

@@

nfl_players %>%
  select(-status, -college_name)

@@

subsetRows <- c(1,3,5)

@@

nfl_players %>%
  filter(position_group == "RB")

@@

nfl_players[c(1,3,5), c(1,2,3)]
nfl_players[subsetRows, subsetVars]
nfl_players[which(nfl_players$position_group == "RB"), subsetVars]
```

@@

nfl_players %>%
  filter(position_group == "RB") %>%
  select(all_of(subsetVars))
```

@@

```{r}
dim(nfl_actualStats_offense_weekly)

@@

```{r}
dim(nfl_players)

@@

fullJoinData <- full_join(
  nfl_actualStats_offense_weekly,
  nfl_players,
  by = c("player_id" = "gsis_id"))

dim(fullJoinData)
```

@@

leftJoinData <- left_join(
  nfl_actualStats_offense_weekly,
  nfl_players,
  by = c("player_id" = "gsis_id"))

dim(leftJoinData)
```

@@

rightJoinData <- right_join(
  nfl_actualStats_offense_weekly,
  nfl_players,
  by = c("player_id" = "gsis_id"))

dim(rightJoinData)
```

@@

innerJoinData <- inner_join(
  nfl_actualStats_offense_weekly,
  nfl_players,
  by = c("player_id" = "gsis_id"))

dim(innerJoinData)
```

@@

semiJoinData <- semi_join(
  nfl_actualStats_offense_weekly,
  nfl_players,
  by = c("player_id" = "gsis_id"))

dim(semiJoinData)
```

@@

antiJoinData <- anti_join(
  nfl_actualStats_offense_weekly,
  nfl_players,
  by = c("player_id" = "gsis_id"))

dim(antiJoinData)
```

@@

crossJoinData <- cross_join(
  unique(nfl_actualStats_offense_weekly[,c("player_id","player_display_name")]),
  data.frame(season = 2020:2024))

@@

dataLong <- nfl_actualStats_offense_weekly %>% 
  select(player_id, player_display_name, season, week, fantasy_points)

dim(dataLong)
```

@@

dataWide <- dataLong %>% 
  pivot_wider(
    names_from = c(season, week),
    names_glue = "{.value}_{season}_week{week}",
    values_from = fantasy_points)

dim(dataWide)
```

@@

dataWide <- nfl_actualStats_offense_weekly %>% 
  select(player_id, player_display_name, season, week, recent_team, opponent_team)

dim(dataWide)
```

@@

dataLong <- dataWide %>% 
  pivot_longer(
    cols = c(recent_team, opponent_team),
    names_to = "role",
    values_to = "team")

dim(dataLong)
```
